---
title: "scratch 2"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
date: "2025-05-29"
---

# Introduction
```{r}
train <- read.csv("C:/Users/Jinxi Zhang/Desktop/project/training_data.csv", stringsAsFactors=FALSE)
test  <- read.csv("C:/Users/Jinxi Zhang/Desktop/project/test_data.csv",  stringsAsFactors=FALSE)

dim(train)  # 1120 × 11
dim(test)   #  280 × 10

sapply(train, function(x) sum(is.na(x)))

# Check ranges
summary(train$Age)                              # look for negative/odd ages

```


# EDA
The histogram gets us a quick picture of how applicants' ages are spread -- are most between 20-30, 40-50. is there a tail of very young or very old borrowers? These questions matter for credit risk prediction because age often correlates with experience, income stability, or risk appetite. If there is a cluster of defaults among very young(<25) applicants, that would be an important observation to make.  

In the histogram, we observed that there is a bulk of loans that sits in the $1000-$4000, but there is a long tail stretching past $15000.This could suggests that log transformation on credit.amount or something similar could be feasible so that the differences among the smaller, more common loans are not washed out by extreme values.

In the boxplot, we observed that "bad" borrowers have a median loan of around $3000. "Good" borrowers have a median loan of around $2500. The IQR for bad loans is shifted upward and is wider, meaning not only are bad borrowers taking larger loans on average, but their loan sizes vary more. So from here, we can already see that loan size clearly differentiates risk: a borrower is more likely to fail to repay their loan if the loan amount is large. Hence, this should be something to pay attention to while constructing the model.
```{r}
## univariate
library(ggplot2)

# Histogram of CreditAmount
ggplot(train, aes(Credit.amount)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  theme_minimal() +
  labs(title = "Distribution of Loan Amounts", x = "Credit Amount", y = "Count")

# Boxplot of CreditAmount by Risk
ggplot(train, aes(x = Risk, y = Credit.amount, fill = Risk)) +
  geom_boxplot(alpha = 0.7) +
  theme_minimal() +
  labs(title = "Loan Amounts by Risk Category", x = "Risk", y = "Credit Amount")
              
                   
```
In this subsection, we investigate pairs of variables to see how they relate. Once we have inspected each variable on its own, the next step is bivariate exploration which means that we pair each predictor with our target (Risk) to seee which features truly move the needle on default probability. The goals of this subsection has three purposes: 
1) find which variables differ meaningfully between "good" and "bad" loans. 
2) Decide on transformations on observede patterns if needed
3) choosee appropriate algorithms 

The first purpose will be achieved via using class balance. It is essentially a simple bar chart of how many loans are labeled "good" vs. "bad." We saw from the histogram that there are 560 "bad" loans and 560 "good" loans, which we considered perfectly balanced thus not needing to perform class weights or threshold adjustments. 

The second purpose will be achieved via exploring the numeric features by risk which includes Age, Duration(Months), and Credit.amount. If "bad" loans have a higher median (credit.amount) or longer Duration, that variable is a likely candidate for prediction. In our results, we see that the for Age, bad loans have a mean of 33.85 years while good loans have a mean of 36.5 years with a p-value of 0.0001. This suggests that good borrowers are on average about 2.6 years older-a small but statistically significant difference. To be more specific, age conveys some risk signal which suggests it can be included in the model.

For Duration, bad loans have a mean of 25.02 months and good loans have a mean of 18.90 months with a p-value of 2.2e-16. This suggests that defaulting borrowers take substantially longer loans which is about 6 months more on average. Both are statistically significant. Putting it into context, longer duration loans carry more uncertainty over time, so this variable will be included in the model.

For Credit.amount, bad loans have a mean of 3905.93 dollars and good loans have a mean of 2931.17 dollars. This suggests that bad borrowers take out about 1000 dollars larger loans on average which is a clear effect. Thus, we see that loan size is a strong predictor of default.

Now, we move on to examining categorical features vs. Risk. We will achieve comparing categorical variables using Pearson's chi-squared test/Fisher's Exact test. Pearson's chi-squared test compares the observed counts in each cell of a contingency table (e.g. number of renters who default vs. don't) to the expectede counts if the two variables were completely unrelated. The results for the chi-squared tests for each is displayed below:

Sex has a p-value of 0.0043 which means it is statistically significant. This suggests that females are under-represented among bad loans so sex carries signal.

Job has a p-value of 0.6512 which means it is not statistically significant. This means that there are no meaningful difference. We could considered dropping it from the model.

Housing has a p-calue of 4.68e-09 which means that it is statistically significant. This suggests that Housing is statistically significant. It means that renters and "freee" lots are over-represented among bad borrowers.

Saving.accounts has a p-value of 6.33e-10 which means it is statistically significant. It means that poorer savings correlate strongly with default risk.

checking.account has a p-value of <2.2e-16 which means it is statistically significant. It measn that checking balance level is highly predictive of default.

Purpose has a p-value of 0.0045 which is statistically significant. It means that certain purposes(e.g. education, funiture) skew toward one risk group

So, we keep Sex, Housing, saving.accounts, checking account, purpose.


```{r}
## bivariate(risk)
# Bar chart of class balance
library(ggplot2)
ggplot(train, aes(Risk)) +
  geom_bar(fill = "steelblue") +
  theme_minimal() +
  labs(title = "Count of Good vs. Bad Loans", x = "Risk", y = "Count")                          

# 2. Numeric vs. Risk: Age, Duration, Credit.amount
for (v in c("Age", "Duration", "Credit.amount")) {
  p <- ggplot(train, aes_string(x = "Risk", y = v, fill = "Risk")) +
    geom_boxplot(alpha = 0.7) +
    theme_minimal() +
    labs(title = paste(v, "by Risk"), x = "Risk", y = v)
  print(p)
  
  # t-test to check if means differ significantly
  tt <- t.test(as.formula(paste(v, "~ Risk")), data = train)
  print(tt)
}

# 3. Categorical vs. Risk: Sex, Job, Housing, Saving.accounts, Checking.account, Purpose
for (v in c("Sex", "Job", "Housing", "Saving.accounts", "Checking.account", "Purpose")) {
  tbl <- table(train[[v]], train$Risk, useNA = "ifany")
  cat("\n\nVariable:", v, "\n")
  print(tbl)
  
  # Use χ² when all expected counts ≥ 5; otherwise Fisher’s exact
  chi <- chisq.test(tbl)
  if (all(chi$expected >= 5)) {
    print(chi)
  } else {
    print(fisher.test(tbl))
  }
}
```

In the above section, we discussed how each feature's relationship with the target (Risk). In this section we construct a correlation plot that measures how the numeric features re
```{r}
## correlation & multivariate
library(corrplot)
library(dplyr)
num_vars <- train %>% select(Age, Duration, Credit.amount)
M <- cor(num_vars)
corrplot(M, method="ellipse")                                          

```
# checking skewness
```{r check-skewness, fig.keep='all', fig.show='hold'}
library(ggplot2)

# Define the numeric columns
nums <- c("Age", "Duration", "Credit.amount")

for (v in nums) {
  # Histogram + density
  p <- ggplot(train, aes_string(x = v)) +
       geom_histogram(aes(y = ..density..), bins = 30,
                      fill = "steelblue", color = "white") +
       geom_density(color = "darkred", size = 1) +
       theme_minimal() +
       labs(title = paste("Histogram + Density:", v),
            x = v, y = "Density")
  print(p)                     # force ggplot to render
  
  # Q–Q plot
  print(                      # wrap in print() just to be safe
    {
      qqnorm(train[[v]], main = paste("Q–Q Plot:", v))
      qqline(train[[v]], col = "red", lwd = 2)
    }
  )
}
```

# Preprocessing
```{r}

# 1. Fix missing values in categorical variables
cat("Checking for empty strings in categorical variables...\n")
cat("Empty Saving.accounts:", sum(train$Saving.accounts == ""), "\n")
cat("Empty Checking.account:", sum(train$Checking.account == ""), "\n")

# Replace empty strings with "unknown"
train$Saving.accounts[train$Saving.accounts == ""] <- "unknown"
train$Checking.account[train$Checking.account == ""] <- "unknown"
test$Saving.accounts[test$Saving.accounts == ""] <- "unknown"
test$Checking.account[test$Checking.account == ""] <- "unknown"

# 2. Check and fix data consistency
# Trim whitespace and standardize case for categorical variables
train$Sex <- trimws(train$Sex)
train$Housing <- trimws(train$Housing)
train$Purpose <- trimws(train$Purpose)
test$Sex <- trimws(test$Sex)
test$Housing <- trimws(test$Housing)
test$Purpose <- trimws(test$Purpose)

# 3. Handle outliers (optional - only if you want to cap extreme values)
# Check for extreme outliers first
Q1 <- quantile(train$Credit.amount, 0.25)
Q3 <- quantile(train$Credit.amount, 0.75)
IQR <- Q3 - Q1
extreme_threshold <- Q3 + 3 * IQR
cat("Credit amounts above", extreme_threshold, "will be capped\n")
cat("Number of extreme outliers:", sum(train$Credit.amount > extreme_threshold), "\n")


train$Credit.amount[train$Credit.amount > extreme_threshold] <- extreme_threshold
test$Credit.amount[test$Credit.amount > extreme_threshold] <- extreme_threshold

# 4. Combine rare categories
purpose_counts <- table(train$Purpose)
rare_purposes <- names(purpose_counts[purpose_counts < 20])
cat("Rare purpose categories:", rare_purposes, "\n")
train$Purpose[train$Purpose %in% rare_purposes] <- "other"
test$Purpose[test$Purpose %in% rare_purposes] <- "other"

# 5. Create derived features based on EDA insights
train$LoanRiskScore <- ifelse(
  train$Duration > 24 & 
  train$Credit.amount > 3500 & 
  train$Checking.account %in% c("unknown", "little"),
  1, 0
)
test$LoanRiskScore <- ifelse(
  test$Duration > 24 & 
  test$Credit.amount > 3500 & 
  test$Checking.account %in% c("unknown", "little"),
  1, 0
)

cat("\nData cleaning completed!\n")

# NOW CONTINUE WITH YOUR EDA SECTION...
# EDA
# The histogram gets us a quick picture...
# UNIFIED CREDIT RISK MODELING APPROACH
# Goal: Predict good vs bad credit risks with consistent, explainable methods

library(dplyr)
library(caret)
library(ranger)
library(pROC)


# =============================================================================
# STEP 1: PREPROCESSING FUNCTION (Same for all data)
# =============================================================================

preprocess_credit_data <- function(train, is_training = TRUE, scaling_params = NULL) {
  # 1. Create log-transformed features for skewed numeric variables
  processed_data <- train %>%
    mutate(
      LogCreditAmt = log1p(Credit.amount),
      LogDuration = log1p(Duration),
      LoanRiskScore = LoanRiskScore  # Include the new feature
    )
  
  # 2. Convert categorical variables to factors
  # WHY: R needs factors for proper dummy variable creation
  processed_data <- processed_data %>%
    mutate(across(
      c(Sex, Housing, Saving.accounts, Checking.account, Purpose),
      factor
    ))
  
  # 3. Create dummy variables (one-hot encoding)
  # WHY: Most ML algorithms need numeric inputs
  processed_data <- processed_data %>%
    fastDummies::dummy_cols(
      select_columns = c("Sex", "Housing", "Saving.accounts", 
                        "Checking.account", "Purpose"),
      remove_first_dummy = TRUE,        # Avoid multicollinearity
      remove_selected_columns = TRUE
    )
  
  # 4. Select final features
  feature_cols <- c("Age", "LogCreditAmt", "LogDuration", "LoanRiskScore",
                    names(processed_data)[grepl("^(Sex_|Housing_|Saving\\.accounts_|Checking\\.account_|Purpose_)", 
                                                names(processed_data))])
  if("Risk" %in% names(processed_data)) {
    processed_data <- processed_data %>% select(all_of(feature_cols), Risk)
  } else {
    processed_data <- processed_data %>% select(all_of(feature_cols))
  }
  
  # 5. Scale numeric features
  # WHY: Different scales can bias algorithms like logistic regression
  numeric_cols <- c("Age", "LogCreditAmt", "LogDuration")
  
  if(is_training) {
    # For training: calculate scaling parameters
    scaling_params <- list()
    for(col in numeric_cols) {
      scaling_params[[col]] <- list(
        mean = mean(processed_data[[col]], na.rm = TRUE),
        sd = sd(processed_data[[col]], na.rm = TRUE)
      )
      # Apply scaling
      processed_data[[col]] <- scale(processed_data[[col]])[,1]
    }
    attr(processed_data, "scaling_params") <- scaling_params
    
  } else {
    # For testing: use training scaling parameters
    if(is.null(scaling_params)) stop("Need scaling parameters for test data")
    for(col in numeric_cols) {
      processed_data[[col]] <- (processed_data[[col]] - scaling_params[[col]]$mean) / 
                               scaling_params[[col]]$sd
    }
  }
  
  # 6. Prepare target variable if present
  if("Risk" %in% names(processed_data)) {
    processed_data <- processed_data %>%
      mutate(Risk = factor(Risk, levels = c("bad", "good")))
  }
  
  return(processed_data)
}

# =============================================================================
# STEP 2: APPLY PREPROCESSING TO TRAINING DATA
# =============================================================================

# Preprocess training data
train_processed <- preprocess_credit_data(train, is_training = TRUE)
scaling_params <- attr(train_processed, "scaling_params")

cat("Training data processed. Shape:", dim(train_processed), "\n")
cat("Features:", setdiff(names(train_processed), "Risk"), "\n\n")

# =============================================================================
# STEP 3: MODEL DEVELOPMENT AND VALIDATION
# =============================================================================

set.seed(42)

# Split training data for validation (80/20)
# WHY: Need to test model performance before final predictions
train_idx <- createDataPartition(train_processed$Risk, p = 0.8, list = FALSE)
tr_data   <- train_processed[train_idx, ]
val_data  <- train_processed[-train_idx, ]

# Set up cross-validation
# WHY: Cross-validation gives more robust performance estimates
ctrl <- trainControl(
  method = "cv",
  number = 5,
  summaryFunction = twoClassSummary,
  classProbs = TRUE,
  savePredictions = "final"
)

# Model 1: Logistic Regression
# WHY: Interpretable baseline, good for understanding feature importance
cat("Training Logistic Regression...\n")
set.seed(42)
log_mod <- train(
  Risk ~ .,
  data = tr_data,
  method = "glm",
  family = binomial,
  metric = "ROC",
  trControl = ctrl
)

# Model 2: Random Forest
# WHY: Handles non-linear relationships, feature interactions automatically
cat("Training Random Forest...\n")
set.seed(42)
rf_mod <- train(
  Risk ~ .,
  data = tr_data,
  method = "ranger",
  metric = "ROC",
  tuneLength = 5,
  trControl = ctrl
)

# =============================================================================
# STEP 4: MODEL COMPARISON ON VALIDATION SET
# =============================================================================

# Predict on validation set
val_pred_log <- predict(log_mod, val_data, type = "prob")[, "bad"]
val_pred_rf  <- predict(rf_mod, val_data, type = "prob")[, "bad"]

# Calculate performance metrics
auc_log <- roc(val_data$Risk, val_pred_log)$auc
auc_rf  <- roc(val_data$Risk, val_pred_rf)$auc

# Class predictions at 0.5 threshold
class_pred_log <- factor(ifelse(val_pred_log > 0.5, "bad", "good"), levels = c("bad", "good"))
class_pred_rf  <- factor(ifelse(val_pred_rf > 0.5, "bad", "good"), levels = c("bad", "good"))

cm_log <- confusionMatrix(class_pred_log, val_data$Risk, positive = "bad")
cm_rf  <- confusionMatrix(class_pred_rf, val_data$Risk, positive = "bad")

# Results summary
results_summary <- tibble(
  Model = c("Logistic Regression", "Random Forest"),
  AUC = c(auc_log, auc_rf),
  Sensitivity = c(cm_log$byClass["Sensitivity"], cm_rf$byClass["Sensitivity"]),
  Specificity = c(cm_log$byClass["Specificity"], cm_rf$byClass["Specificity"]),
  F1 = c(cm_log$byClass["F1"], cm_rf$byClass["F1"])
)

cat("\n=== MODEL COMPARISON RESULTS ===\n")
print(results_summary)

# Choose best model (you can change this logic)
best_model <- if(auc_rf > auc_log) rf_mod else log_mod
best_model_name <- if(auc_rf > auc_log) "Random Forest" else "Logistic Regression"

cat("\nBest model:", best_model_name, "\n")

# =============================================================================
# STEP 5: FINAL MODEL TRAINING ON ALL TRAINING DATA
# =============================================================================

cat("\nRetraining best model on full training dataset WITH SMOTE...\n")

# Use the SAME control with SMOTE for final model
ctrl_final <- trainControl(
  method = "cv",
  number = 3,  # Fewer folds for final training
  summaryFunction = twoClassSummary,
  classProbs = TRUE,
  sampling = "smote"  # CRITICAL: Include SMOTE here too
)

set.seed(42)
final_model <- train(
  Risk ~ .,
  data = train_processed,
  method = best_model$method,
  tuneGrid = data.frame(best_model$bestTune),
  trControl = ctrl_final  # Use SMOTE control instead of "none"
)

cat("Final model training complete with SMOTE\n")
# =============================================================================
# STEP 6: FINAL PREDICTIONS ON TEST DATA
# =============================================================================

cat("Processing test data and making final predictions...\n")

# Preprocess test data using SAME scaling parameters as training
test_processed <- preprocess_credit_data(test, is_training = FALSE, scaling_params = scaling_params)

# Make predictions with error handling
final_predictions <- predict(final_model, test_processed)

# Initialize probability variables
prob_bad <- NULL
prob_good <- NULL

# Try to get probabilities with error handling
tryCatch({
  final_probabilities <- predict(final_model, test_processed, type = "prob")
  
  # Check what columns are available
  if("bad" %in% names(final_probabilities)) {
    prob_bad <<- final_probabilities$bad
    prob_good <<- final_probabilities$good
  } else if("good" %in% names(final_probabilities)) {
    prob_good <<- final_probabilities$good
    prob_bad <<- 1 - prob_good
  } else {
    # Use first two columns if column names don't match
    prob_bad <<- final_probabilities[, 1]
    prob_good <<- final_probabilities[, 2]
  }
  
  cat("Probability prediction successful\n")
  
}, error = function(e) {
  cat("Probability prediction failed, using class predictions only\n")
  prob_bad <<- ifelse(final_predictions == "bad", 1, 0)
  prob_good <<- ifelse(final_predictions == "good", 1, 0)
})

# Create results dataframe
final_results <- data.frame(
    ID = test$ID,  # Use the ORIGINAL IDs from test data
    Predicted_Risk = final_predictions,
    Probability_Bad = prob_bad,
    Probability_Good = prob_good
)

cat("\n=== FINAL PREDICTIONS SUMMARY ===\n")
cat("Total predictions:", nrow(final_results), "\n")
cat("Predicted 'bad' risks:", sum(final_predictions == "bad"), "\n")
cat("Predicted 'good' risks:", sum(final_predictions == "good"), "\n")

cat("\nFirst 10 predictions:\n")
print(head(final_results, 10))

cat("\n=== PROJECT COMPLETE ===\n")
cat("Model used:", best_model_name, "\n")
cat("Consistent preprocessing applied throughout\n")
cat("Ready for interpretation and reporting\n")
```
```{r}
# FINAL MODEL PERFORMANCE EVALUATION
# Now we can see how well our model actually performed!

library(dplyr)
library(caret)
library(pROC)

# Read the answer key
true_labels <- read.csv("C:/Users/Jinxi Zhang/Desktop/project/kaggle_sample_solution_file.csv")

# Check the structure
head(true_labels)
cat("Answer key contains", nrow(true_labels), "entries\n")

# Make sure the Risk column has the same factor levels as our model
true_labels$Risk <- factor(true_labels$Risk, levels = c("bad", "good"))

# Assuming your final_results dataframe from the previous code has:
# - ID: row identifier
# - Predicted_Risk: your model's predictions
# - Probability_Bad: probability of bad credit

# Check dimensions
cat("Final results rows:", nrow(final_results), "\n")
cat("True labels rows:", nrow(true_labels), "\n")
cat("True labels ID range:", min(true_labels$ID), "to", max(true_labels$ID), "\n\n")

# The answer key only contains a subset of test cases
# We need to match by the ID column from the answer key

evaluation_data <- true_labels %>%
  left_join(final_results, by = "ID") %>%
  filter(!is.na(Predicted_Risk)) %>%  # Keep only cases where we have predictions
  select(ID, Risk, Predicted_Risk, Probability_Bad) %>%
  rename(True_Risk = Risk)

# Remove any rows where we don't have true labels
evaluation_data <- evaluation_data %>% 
  filter(!is.na(True_Risk))

cat("Evaluation dataset contains", nrow(evaluation_data), "cases\n\n")

# =============================================================================
# PERFORMANCE METRICS
# =============================================================================

# 1. ACCURACY
accuracy <- mean(evaluation_data$True_Risk == evaluation_data$Predicted_Risk)
cat("=== OVERALL PERFORMANCE ===\n")
cat("Accuracy:", round(accuracy * 100, 1), "%\n")

# 2. CONFUSION MATRIX
cm <- confusionMatrix(
  evaluation_data$Predicted_Risk, 
  evaluation_data$True_Risk, 
  positive = "bad"
)

print(cm)

# 3. AUC (if probabilities are available)
if(!all(evaluation_data$Probability_Bad %in% c(0, 1))) {
  auc_score <- roc(evaluation_data$True_Risk, evaluation_data$Probability_Bad)$auc
  cat("\n=== AUC SCORE ===\n")
  cat("AUC:", round(auc_score, 3), "\n")
  
  # Plot ROC curve
  roc_obj <- roc(evaluation_data$True_Risk, evaluation_data$Probability_Bad)
  plot(roc_obj, main = paste("ROC Curve (AUC =", round(auc_score, 3), ")"))
}

# 4. DETAILED BREAKDOWN
cat("\n=== DETAILED BREAKDOWN ===\n")
cat("Total test cases:", nrow(evaluation_data), "\n")
cat("Correctly predicted 'bad' risks:", 
    sum(evaluation_data$True_Risk == "bad" & evaluation_data$Predicted_Risk == "bad"), 
    "out of", sum(evaluation_data$True_Risk == "bad"), "\n")
cat("Correctly predicted 'good' risks:", 
    sum(evaluation_data$True_Risk == "good" & evaluation_data$Predicted_Risk == "good"), 
    "out of", sum(evaluation_data$True_Risk == "good"), "\n")

# 5. BUSINESS INTERPRETATION
sensitivity <- cm$byClass["Sensitivity"]  # True Positive Rate
specificity <- cm$byClass["Specificity"]  # True Negative Rate

cat("\n=== BUSINESS INTERPRETATION ===\n")
cat("Sensitivity (recall for 'bad' risks):", round(sensitivity * 100, 1), "%\n")
cat("- This means we correctly identified", round(sensitivity * 100, 1), "% of truly bad credit risks\n")
cat("Specificity (recall for 'good' risks):", round(specificity * 100, 1), "%\n")
cat("- This means we correctly identified", round(specificity * 100, 1), "% of truly good credit risks\n")

# 6. SAMPLE OF CORRECT/INCORRECT PREDICTIONS
cat("\n=== SAMPLE PREDICTIONS ===\n")
cat("First 10 predictions vs actual:\n")
sample_results <- evaluation_data %>%
  select(ID, True_Risk, Predicted_Risk, Probability_Bad) %>%
  mutate(
    Correct = True_Risk == Predicted_Risk,
    Probability_Bad = round(Probability_Bad, 3)
  ) %>%
  head(10)

print(sample_results)

# 7. SUMMARY STATISTICS
correct_predictions <- sum(evaluation_data$True_Risk == evaluation_data$Predicted_Risk)
total_predictions <- nrow(evaluation_data)

cat("\n=== FINAL SUMMARY ===\n")
cat("Model:", best_model_name, "\n")
cat("Correct predictions:", correct_predictions, "out of", total_predictions, "\n")
cat("Final accuracy:", round(accuracy * 100, 1), "%\n")

# Determine if the model performed well
if(accuracy > 0.8) {
  cat("🎉 Excellent performance! Your model is doing very well.\n")
} else if(accuracy > 0.7) {
  cat("✅ Good performance! Your model is reasonably accurate.\n")
} else if(accuracy > 0.6) {
  cat("⚠️  Moderate performance. There's room for improvement.\n")
} else {
  cat("❌ Low performance. Consider different features or algorithms.\n")
}

cat("\nFor a credit risk model, both sensitivity and specificity are important:\n")
cat("- High sensitivity = catch most bad credit risks (reduce defaults)\n")
cat("- High specificity = don't reject too many good customers (maintain business)\n")
```



